Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-09-18 paper/paper.Rmd
omit checkerboard plot, remove resolvec comments

<!--

##### Option: selection = "checkerboard"

-->

@@

<!--
AB:
The text previously stated that the range argument is ignored. This can't be true, there must be some argument that controls the size of checkerboard fields.
-->

<!--
AB: Checkerboard pattern is just a special case of a systematic pattern and likely not of great practical relevance because there are only two folds -> omit figure.

```{r block-checkerboard, fig.cap='Checkerboard resampling of square spatial blocks using the implementation in package blockCV (method "spcv\\_block" with option selection = "checkerboard" in mlr3spatiotempcv). The size of the squares is 1000 m, and eleven out of the 19 blocks were assigned to this test sample.', out.width="40%", fig.pos="ht!"}
rsmp_block_checkerboard = rsmp("spcv_block",
  range = 1000, folds = 2,
  selection = "checkerboard")

autoplot(rsmp_block_checkerboard,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

-->

<!--
AB: This figure and subsubsubsection takes up a lot of space for very little additional information.

```{r block-rows-and-cols, fig.cap='Random resampling of a specifid number of rectangular blocks as implemented in package blockCV (method "spcv\\_block" in mlr3spatiotempcv with arguments rows = 6 and cols = 3).', out.width="40%", fig.pos="ht"}
rsmp_block_rows_cols = rsmp("spcv_block",
  rows = 6, cols = 3, folds = 5
)

autoplot(rsmp_block_rows_cols,
  size = 0.8, fold_id = 1, task = task,
  show_blocks = TRUE, show_labels = TRUE) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```

\newpage

-->

@@

<!-- TODO: AB: should be combined with the previous figure into a two-panel figure. Differences are much easier to recognize if plotted next to each other. -->
```{r env-1-eval, fig.cap='Environmental leave-one-block-out CV from package blockCV using one (left, "distdeforest") and two (right, "distdeforest" and "slope") predictors to define blocks in the feature space.', out.width="100%", fig.pos="ht", echo=FALSE}
rsmp_env = rsmp("spcv_env",
  features = "distdeforest", folds = 5)

@@

library("patchwork")
plot_env_single + plot_env_multi + plot_layout(guides = 'collect')
```
<!-- AB: TODO: In general, the code would look much simpler if we could get rid of the scale_x/y_continuous() calls. Improve default settings of autoplot()? -->

@@

<!-- spcv_block: how to set argument `theRange` -->
<!-- AB: argument is actually called range, not theRange -->
Method `"spcv_block"` requires the user to supply a value for argument `range` which denotes the block size used to create the blocking scheme across the study area.
This specification is non-trivial and therefore package \pkg{blockCV} provides some helper functions (`spatialAutoRange()` and `rangeExplorer()`) to conduct a data-driven estimation of the distance at which the spatial autocorrelation in the data levels off [@blockCV].
According to the package authors, this estimate should then be used for argument `range` to have a sensible value for the block sizes created in method `"spcv_block"`.
Rectangular partitioning can be problematic in irregularly shaped study areas where some of the resulting partitions may contain substantially fewer observations than others.

>>>>

@@

@@

```{r env-1-eval, fig.cap='Environmental leave-one-block-out CV from package blockCV using one (left, "distdeforest") and two (right, "distdeforest" and "slope") predictors to define blocks in the feature space.', out.width="100%", fig.pos="ht", echo=FALSE}
rsmp_env = rsmp("spcv_env",
  features = "distdeforest", folds = 5)

@@

library("patchwork")
plot_env_single + plot_env_multi + plot_layout(guides = 'collect')
```

@@

<!-- spcv_block: how to set argument `range`` -->
Method `"spcv_block"` requires the user to supply a value for argument `range` which denotes the block size used to create the blocking scheme across the study area.
This specification is non-trivial and therefore package \pkg{blockCV} provides some helper functions (`spatialAutoRange()` and `rangeExplorer()`) to conduct a data-driven estimation of the distance at which the spatial autocorrelation in the data levels off [@blockCV].
According to the package authors, this estimate should then be used for argument `range` to have a sensible value for the block sizes created in method `"spcv_block"`.
Rectangular partitioning can be problematic in irregularly shaped study areas where some of the resulting partitions may contain substantially fewer observations than others.
